\documentclass{article}

\usepackage{fullpage}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{url}
\usepackage{latexsym}
\usepackage{paralist}


% settings for algorithm2e psuedocode style
\usepackage[procnumbered, ruled, linesnumbered, commentsnumbered, noend]{algorithm2e}
% a few parameters that are set to typeset pseudocode
\SetAlCapNameSty{textsc}
\SetProcNameSty{textsc}
\SetProcArgSty{textsc}

%style for pseudocode comments
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{darkgray}{#1}}
\SetCommentSty{mycommfont}

% used for formatting graphs
\usepackage{tikz}
\usetikzlibrary{arrows}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}


\newcommand{\honor}{\noindent \textbf{Aggie Honor Statement: }On my honor as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the academic work included in this assignment.
}


\newcommand{\checklist}{\noindent\textbf{Checklist:}
Did you...
\begin{compactenum}
\item abide by the Aggie Honor Code?
\item solve all problems?
\item start a new page for each problem?
\item show your work clearly?
\item type your solution?
\item submit a PDF to eCampus?
\end{compactenum}
}

\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set #1}\end{center}}
\newcommand{\duedate}[1]{\begin{quote}\textbf{Due: #1} on eCampus (\url{ecampus.tamu.edu}). \\You must show your work in order to recieve credit.\end{quote}}
\newcommand{\mysectionnumber}[0]{503}

\title{CSCE 222: Discrete Structures for Computing\\Section \mysectionnumber\\Fall 2016}
\author{Joseph Martinsen}

\begin{document}

\maketitle

\problemset{4}

\duedate{25 September 2016 (Sunday) before 11:59 p.m.}

\bigskip

% Sets and Set Operations
\begin{problem} (30 points)\\
Consider the sets $P = (A-B)-C$ and $Q = (A-C) - (B-C)$.\\
Determine which relationship ($\subseteq,=,\supseteq$) holds between the two sets $P$ and $Q$.\\
Your answer will be either $P \subseteq Q$, or $P = Q$, or $P \supseteq Q$.\\
Justify your answer three ways by
\begin{enumerate}
\item drawing the Venn diagram,
\item constructing the membership table, and
\item proving it (using set identities with set builder notation).
\end{enumerate}
\end{problem}

\begin{solution}\ \\


\end{solution}

\newpage

% Sets and Set Operations
\begin{problem} (20 points)\\
Show that if $A$, $B$, and $C$ are sets, then $|A \cup B \cup C| = |A| + |B| + |C| - |A \cup B| - |A \cup C| - |B \cup C| + |A \cap B \cap C|$.
\end{problem}

\begin{solution}\ \\


\end{solution}

\newpage

\bigskip
\honor

\bigskip
\checklist
\end{document}
